\documentclass{article}

% margins
\usepackage[top=1in, bottom=1.5in, left=1.5in, right=1.5in]{geometry}

% smart quotes
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

% line spacing
\usepackage{setspace}
\singlespacing

% tiny bullet points
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

% new list environment for lists with no labels
% documentation on how this works at:
%     run `texdoc source2e`
%     look at section about lists on page 218 
\newenvironment{atomize}
    {\begin{list} {} {
            \setlength\itemindent{0pt}
            \setlength\leftmargin{10pt}
            \setlength\labelwidth{0pt}
    }}
    {\end{list}}

% info for \maketitle
\author{Dylan Holmes, Kuangyou Yao, Jonathan K}
\title{Brooks' law}
\date{February 17$^{th}$, 2014}

% todo checklist
% - - — - - - - - - - - - - — - - - - - - - - - - — - - - - - - - - - - 
% [ ] write more
% - - — - - - - - - - - - - — - - - - - - - - - - — - - - - - - - - - - 

\begin{document}

\maketitle

\section*{Abstract}
According to Brooks' Law, "adding manpower to a late software project makes it later". Brooks' law originated from Fred Brooks' 1975 book, "The Mythical Man-Month", and has since become commonly accepted through out the software development community. 

Suppose in a software firm, a project manager is facing a deadline issue. It is only 1 month away from the proposed deadline for the project in hand. Given that the project is only 60\% done, the project manager faces the problem whether he should hire additional engineers to pace up the process.

Brook’s law argues that by adding new engineers, experienced and efficient engineers will have to give up part of their productivity to train the new people. Such a sacrifice will be devastating to a late project. The late project would be even more behind schedule by the time the new engineers would be able to reach the desirable efficiency. In short, it is not feasible to hire new engineers to rescue a late project.

In "The Mythical Man Month", Brook also includes interesting arguments like inter-employee communication, planning and optimism. In our paper, we will incorporate these ideas to develop a mathematic model that captures the dynamics of a project and employees working for the project.

\section*{Base Case}
    \begin{atomize}
        \item Assumptions:
            \begin{itemize}
                \item Brooks' law can be modelled as the relationships between time, junior staff, senior staff, and progress.
                \item The relationships between these quantites can be modelled as a system of first order differential equations.
                \item Any of these quatities could effect any other quantity besides time.
            \end{itemize}
        \item Quantities:
            \begin{itemize}
                \item [$t$]: time spent working
                \item [$x$]: junior staff
                \item [$y$]: senior staff
                \item [$p$]: progress
            \end{itemize}
        \item Model:
            \begin{atomize}
                \item $x\prime = f\left(x, y, p, t\right)$
                \item $y\prime = g\left(x, y, p, t\right)$
                \item $p\prime = h\left(x, y, p, t\right)$
            \end{atomize}
    \end{atomize}

\section*{Case I: extends Base}
    \begin{atomize}
        \item Assumptions:
            \begin{itemize}
                \item Only Junior staff is added.
                \item Only Senior staff contributes progress.
                \item Junior staff is added as a function of time, at a constant rate.
                \item Junior staff becomes senior staff as a function of time, at a constant rate.
                \item Senior staff contribute progress as a function of time, at a constant rate.
            \end{itemize}
        \item Quantities:
            \begin{itemize}
                \item [$r$]: rate at which junior staff is added
                \item [$s$]: rate at which junior staff becomes senior staff
                \item [$k$]: rate at which senior staff contributes progress
            \end{itemize}
        \item Model:
            \begin{atomize}
                \item $x\prime = r - s$
                \item $y\prime = sx$
                \item $p\prime = ky$
            \end{atomize}
        \item Solution:
            \begin{atomize}
                \item $x = \left(r - s\right)t + x_{0}$
                \item $y = s\left(r - s\right)t + sx_{0}$
                \item $p = \frac{1}{6}ks(r-s)t^{3} + \frac{1}{2}ksx_{0}t^{2} + ky_{0}t + p_{0}$
            \end{atomize}
        \item Interpret:
            \begin{itemize}
                \item Bullshit!
            \end{itemize}
    \end{atomize}


\end{document}

